### 2011-08-13 doc/theses/vitasek/diplomka.tex
Thesis: in progress

@@

TODO types of data:
\begin{itemize}
	\item Realistic 
	\item Realistic with artificial attributes
	\item Artificial
\end{itemize}

TODO for all types, show GraphViz pictures.

@@

\subsection{Realistic data with artificial attributes}

TODO we have taken some of the text data and converted it to attributes like this, A B C

@@

TODO these are random graphs.
TODO talk about how they are created, about their structure.
TODO talk about some "density".

@@

TODO we will be using jInfer and its module AttributeStats see \ref{jInfer} and \ref{attrstats}.
TODO describe how to create a model, describe how we get IGG, link BasicIGG

@@

TODO to the best of our knowledge, this framework is one-of-a-kind

@@

@@

TODO elaborate more, if too short:)

@@

\chapter{Traces}
\label{traces}

>>>>

TODO what are trying to establish? What is our aim here? To get an understanding how the system and its components behave. What do the parameters affect. To see which types of data are best handled by specific algorithms. To see what are the time scales involved in ID search and how various parameters affect the run times of the heuristics.

@@

Let us now talk about the XML data we will be using to conduct out experiments. We are using XML documents of three categories:

\begin{itemize}
	\item Realistic 
	\item Realistic with artificial (converted) attributes
	\item Artificial
\end{itemize}

A short reasoning for this choice: realistic - of course, we want to see the performance in cases taken from the real world. The problem with realistic data is that sometimes, interesting values (that might or might not contain IDs) are stored as text nodes % TODO is this name consistent with what I've been defining?
instead of attributes. We might try to look at such data, convert some of these ``suspicious" values to attributes (e.g. using a smart XSL transformation), let our heuristics find the ID sets, and then translate them back to XML keys (see \ref{realistic-converted} for details).
And finally, we create completely artificial data to create inputs that will really put our heuristics to the test. This is because the realistic data often prove to be quite easy to solve - the list of candidate AMs is usually too short to be hard to solved to optimality.

@@

\begin{figure}
  \caption{Realistic data - first part}
  \label{image-experiments-data-realistic-1}
  \centering
    \subfigure[OVA1]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA1.eps}}
    \subfigure[OVA2]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA2.eps}}
    \subfigure[OVA3]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA3.eps}}
\end{figure}

\begin{figure}
  \caption{Realistic data - second part}
  \label{image-experiments-data-realistic-2}
  \centering
    \subfigure[XMA-c]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMA-c.eps}}
    \subfigure[XMA-p]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMA-p.eps}}
    \subfigure[XMD]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMD.eps}}
\end{figure}

\subsection{Realistic data with artificial attributes}
\label{realistic-converted}

TODO we have taken some of the text data and converted it to attributes like this, A B C.

TODO we can convert it back to keys!

\begin{figure}
  \caption{Realistic data with converted attributes}
  \label{image-experiments-data-converted}
  \centering
    \subfigure[MSH]{\includegraphics[width=0.45\textwidth]{images/experiments/data/converted/MSH.eps}}
    \subfigure[NTH]{\includegraphics[width=0.45\textwidth]{images/experiments/data/converted/NTH.eps}}
\end{figure}

@@

TODO these are random graphs.

TODO talk about how they are created, about their structure.

TODO talk about some "density".

TODO talk about the "size" test data

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
%  	\subfigure[100-100]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-100.eps}}
%	\subfigure[100-200]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-200.eps}}
%    \subfigure[100-1000]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-1000.eps}}    
\end{figure}

@@

TODO describe the actual HW/SW setup: two computers, Windows/Linux, versions etc. What is running when experimenting, that we are always using more runs to counter for effects like caches and stuff that happens. Say many things actually depend on the order in which we run the experiments in one set, and if it is relevant we will talk about it in that particular experiment.

TODO we will be using jInfer and its module AttributeStats see \ref{jInfer} and \ref{attrstats}.

TODO describe how to create a model, describe how we get IGG, link BasicIGG

@@

@@

To the best of our knowledge, at the time of writing this thesis is jInfer the only public, open source and actually working solution for XML schema inference-related tasks.

@@

@@

\chapter{Experimental Trace}
\label{traces}
